Using VDMS to Search 100M Images: A Piece of Cake

### 2020-02-12 yfcc100m/paper/vldb2020/vdms-vldb2020.tex
Update intro and other minor changes
Minor updates on eval
Add acks

We have to acknowledge Philip and Vishakha for help in fixing PMGD bug,
Nilesh for his help/input, and any other reviewer.

>>>>

We would like to thank the many people that made this project possible and
helped us through the process, as this work is the results of many efforts.
We want to thank our managers Nilesh Jain and Ravi Iyer for their
full support and input during the duration of the project.
We want to specially acknowledge Philip Lantz and Vishakha Gupta for their help
with PMGD, key to load large datasets into VDMS.
We want to acknowledge the Intel Labs VDMS team for their efforts
open-sourcing and maintaining the system.
We want to thank Jason Gardner for his helping in setting up many of the servers
and infrastructure needed to conduct our experiments.
